Reionization Planck 2018 Notes

### 2020-06-23 results/notes.tex
Updates from Overleaf

\documentclass[prd,twocolumn,amsmath,amssymb,floatfix,superscriptaddress,nofootinbib]{revtex4-1}
\usepackage{bm}
\usepackage{amsmath}
\usepackage{epsfig}
\usepackage{color}
\usepackage{natbib}
\usepackage{textcase}
\usepackage{graphicx}
\usepackage{ifthen}
\usepackage{xstring}
\usepackage{graphicx}
\usepackage[utf8]{inputenc} 
\usepackage{amssymb}
\usepackage{latexsym}
\usepackage{epstopdf}
\epstopdfsetup{update}
\DeclareGraphicsExtensions{.ps, .png}
\epstopdfDeclareGraphicsRule{.ps}{pdf}{.pdf}{ps2pdf -dEPSCrop -dNOSAFER #1 \OutputFile} 
\usepackage{dcolumn} 
\usepackage{multirow}
\usepackage{appendix}
\usepackage{footnote}
\usepackage{tabularx,ragged2e,booktabs}
\usepackage[normalem]{ulem}
\usepackage{float}
\restylefloat{table}

@@

\title{Reionization Planck 2018 ...}

@@

List of tests:\\
-

\begin{figure}[t]
\includegraphics[width=0.40\textwidth]{../paper/plots/plot_tau_gtz.pdf}
\caption{...
}
\label{fig:}
\end{figure}

\begin{figure}
\includegraphics[width=0.40\textwidth]{python_kde_test/pl18_pc_zmax30_pliklite_srollv2_1015_tau_posterior_fraccov_1p0_burnin_10000_yes_norm_gaussian0p1_0p12_0p14.pdf}
\caption{...
}
\label{fig:}
\end{figure}

>>>>

\documentclass[prd,amsmath,amssymb,floatfix,superscriptaddress,nofootinbib]{revtex4-1}
\usepackage{bm}
\usepackage{amsmath}
\usepackage{epsfig}
\usepackage{color}
\usepackage{natbib}
\usepackage{textcase}
\usepackage{graphicx}
\usepackage{ifthen}
\usepackage{xstring}
\usepackage{graphicx}
\usepackage[utf8]{inputenc} 
\usepackage{amssymb}
\usepackage{latexsym}
\usepackage{epstopdf}
\epstopdfsetup{update}
\DeclareGraphicsExtensions{.ps, .png}
\epstopdfDeclareGraphicsRule{.ps}{pdf}{.pdf}{ps2pdf -dEPSCrop -dNOSAFER #1 \OutputFile} 
\usepackage{dcolumn} 
\usepackage{multirow}
\usepackage{appendix}
\usepackage{footnote}
\usepackage{tabularx,ragged2e,booktabs}
\usepackage[normalem]{ulem}
\usepackage{float}
\restylefloat{table}

@@

\title{Reionization Planck 2018 Notes}

@@

List of tests:\\
\begin{itemize}
    \item {Direct MCMC chains
        \begin{enumerate}
            \item {PC zmax = 30}
            \item {PC zmax = 50}
            \item{tanh tau}
            \item{two-parameter model with taulo and tauhi}
        \end{enumerate}
    }
    \item{best tests
        \begin{enumerate}
            \item {from tanh highz 2-parameter model we found that for tau hi $>$ 0.02, we get ML is tau hi = 0.0206, tau lo = 0.0414 corresponding to zre = 6.29 and xe hi = 0.0748. This model has a -loglike = 499.5458 against the full ML 498.2425 which gives a difference of 2.6 in chi2. (full ML has tau lo = 0.0543, tau hi = 0.00542 corresponding to zre = 7.68 and xe hi = 0.0214. }
            \item{Using above informatiion, we fixed tau hi = 0.02, and ran a best-fit searching for best tau lo and found tau lo = 0.045 (c.f. 0.0414 from chains), together with the fixed tau hi = 0.02, corresponds to zre = 6.67 and xe min = 0.073. The likelihood here is 499.2914, a difference of 2.1 (instead of 2.6) in chi2.}
        \end{enumerate}
        }

\end{itemize}

\begin{figure}
\includegraphics[width=0.65\textwidth]{results/cosmomc_runs/pl18_plots_zmax30/plot_pub_tau_gtz_dz_0p1_pl18_pc_zmax30_pliklite_post_0930_and_pl18_pc_zmax30_pliklite_srollv2_0930.pdf}
\caption{PC chains for zmax = 30. Planck 2018 original lowE vs srollv2 likelihood (plik\_lite\_TTTEEE + lowl + simall\_EE vs plik\_lite\_TTTEEE + lowl + sroll2\_EE).
}
\label{fig:}
\end{figure}

\begin{figure}
\includegraphics[width=0.65\textwidth]{results/cosmomc_runs/pl18_plots_zmax50/plot_pub_tau_gtz_dz_0p1_pl18_pc_zmax50_pliklite_post_and_pl18_pc_zmax50_pliklite_srollv2.pdf}
\caption{PC chains for zmax = 50. Planck 2018 original lowE vs srollv2 likelihood (plik\_lite\_TTTEEE + lowl + simall\_EE vs plik\_lite\_TTTEEE + lowl + sroll2\_EE).
}
\label{fig:}
\end{figure}

\begin{figure}
\includegraphics[width=0.65\textwidth]{results/cosmomc_runs/pl18_plots_zmax30/plot_pub_tau_gtz_dz_0p1_pl18_pc_zmax30_pliklite_post_0930_and_pl18_pc_zmax50_pliklite_post.pdf}
\caption{Comparing zmax = 30 and 50 PC chains using Planck 2018 original lowE likelihood (plik\_lite\_TTTEEE + lowl + simall\_EE). Note that the zmax = 30 uses 5 PCs, whereas the zmax = 50 chains uses 7 PCs.
}
\label{fig:tau_gtz_zmax_30_vs_50_simall_EE}
\end{figure}

\begin{figure}
\includegraphics[width=0.65\textwidth]{results/cosmomc_runs/pl18_plots_zmax30/plot_pub_tau_gtz_dz_0p1_pl18_pc_zmax30_pliklite_srollv2_0930_and_pl18_pc_zmax50_pliklite_srollv2.pdf}
\caption{Same as Fig.~\ref{fig:tau_gtz_zmax_30_vs_50_simall_EE}, but for the srollv2 likelihood (plik\_lite\_TTTEEE + lowl + sroll2\_EE).
}
\label{fig:}
\end{figure}

%Optional
\begin{figure}
\includegraphics[width=0.65\textwidth]{results/cosmomc_runs/pl18_plots_zmax30/plot_pub_tau_gtz_dz_0p1_pl18_pc_zmax30_plikfull_and_pl18_tanh_post_plikfull.pdf}
\caption{PC zmax = 30 vs tanh chains with plik\_full\_TTTEEE for the high-l likelihood.
}
\label{fig:}
\end{figure}

 \begin{figure}
\includegraphics[width=0.65\textwidth]{   results/cosmomc_runs/pl18_plots_zmax30/plot_pub_tau_gtz_dz_0p1_pl18_pc_zmax30_pliklite_srollv2_0930_and_pl18_tanh_post_pliklite_srollv2_with_added_two_parameter_ML_xe_full.pdf}
\caption{PC zmax = 30 vs tanh chains with plik lite and srollv2, with ML model from two-parameter model for tau hi restricted to $>$ 0.02 (ML model: tau hi = 0.0206, tau lo = 0.0414).
}
\label{fig:two_parameter_model_ML}
\end{figure}

\begin{figure}
\includegraphics[width=0.65\textwidth]{  results/cosmomc_runs/pl18_plots_zmax30/plot_pub_tau_gtz_dz_0p1_pl18_pc_zmax30_pliklite_srollv2_0930_and_pl18_tanh_post_pliklite_srollv2_with_added_two_parameter_ML_PC_proj.pdf}
\caption{Same as Fig.~\ref{fig:two_parameter_model_ML} except the blue curve is a PC projection instead of the full xe(z) of the model.
}
\label{fig:}
\end{figure}

 \begin{figure}
\includegraphics[width=0.65\textwidth]{    results/cosmomc_runs/two_parameter_model/plot_1D_tau_hi_pl18_tanh_highz_fixed_taulo_test2_run1.pdf
}
\caption{
}
\label{fig:}
\end{figure}

\begin{figure}
\includegraphics[width=0.65\textwidth]{python_kde_test/pl18_pc_zmax30_pliklite_srollv2_1015_tau_posterior_fraccov_1p0_burnin_10000_yes_norm_gaussian0p1_0p12_0p14.pdf}
\caption{KDE tests in python for the tanh model with various f = 0.1, 0.12, 0.14. It is probably safest to use any of these, so given the smaller f the better, f = 0.1 is probably the best choice here.
}
\label{fig:}
\end{figure}
